---
title: "RAPID Question Bank Dashboard"
date: "Last Updated: 01/27/2021"
output: 
  html_document:
    css: "custom2.css"
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  comment = NA,
  warning = FALSE,
  message = FALSE)
```

<p style="font-size:14pt">This site hosts a list of questions asked as a part of the RAPID-EC project. All efforts were taken to ensure the accuracy of the question sources.</p>

<p style="font-size:14pt">If there are any questions or concerns, please do not hesitate to reach out to the RAPID-EC team.</p>

```{r packages, echo=FALSE, warning=FALSE, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(knitr)
library(tidyr)
library(kableExtra)
library(stringr)
library(dplyr)
options(knitr.table.format = "html", knitr.kable.NA = '') 
```

```{r read data, echo=FALSE}
data.raw <- read_excel("Data/SurveyTrackingCalendar.xlsx")
data.raw$'Modules / Special Topic Implemented' <- gsub(pattern = "\n", replacement = "<br/>", x = data.raw$'Modules / Special Topic Implemented')

data.raw2 <- read_excel("Data/ModuleKey.xlsx")
data.raw2$'Go to Module' <- paste0("<a href='",data.raw2$'Go to Module',"'>", data.raw2$'Go to Module',"</a>")

```

## Survey Calendar and Module Key {.tabset}

### Survey Calendar

<p style="font-size:14pt">Baseline Survey = Survey that participants take when first participating</p>
<p style="font-size:14pt">Follow-Up Survey = Participants are invited to a follow-up survey that contains some core items from baseline and additonal module items</p>
```{r display data, echo=FALSE}

DT::datatable(data.raw, class = 'cell-border stripe hover',  rownames = F,  options = list(
  pageLength = 10, autoWidth = TRUE
), escape = FALSE)
```
### Module Key
<p style="font-size:14pt; font-weight:bold">Module Key</p>
<p style="font-size:14pt">We began using a module system to our follow-up surveys starting week 33. Before week 33, some of the modules were special topics. Below is a key that provides a brief summary of each module as well as a link to the questions for that module on the site. You can also use the navigation bar to switch between modules.</p>
```{r display data 2, echo=FALSE}

DT::datatable(data.raw2, class = 'cell-border stripe hover',  rownames = F,  options = list(
  pageLength = 20, autoWidth = TRUE
), escape = FALSE)
```
## {-}


