---
title: "RAPID-EC Question Bank"
output: 
  html_document:
    css: "custom2.css"
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  comment = NA,
  warning = FALSE,
  message = FALSE)
```

![RAPID-EC Project](~/Dropbox (University of Oregon)/RAPID-EC/Data Management R3/EE_R3 Question Bank/Data/QBPIC.png)

<p style="font-size:14pt">This site hosts a list of questions asked as a part of the RAPID-EC project. All efforts were taken to ensure the accuracy of the question sources.</p>

<p style="font-size:14pt">Use the menu above to navigate between our household (EC) survey questions and our childcare provider (CC) survey questions.</p>

<p style="font-size:14pt">If there are any questions or concerns, please do not hesitate to reach out to the RAPID-EC team.</p>

<p style="font-size:14pt">Suggested citation (APA7): 
Center for Translational Neuroscience, Stanford University. (n.d.). Rapid-EC Survey. RAPID-EC Question Bank. Retrieved DATE, from https://r3questionbank.netlify.app/  </p>


```{r packages, echo=FALSE, warning=FALSE, include=FALSE, cache=FALSE}

```

```{r read data, echo=FALSE}


```


```{r display data 2, echo=FALSE}


```



